Medical Concept Extraction

### 2012-12-16 paper/paper.tex
Recovring sections that were accidentally deleted.

\begin{figure*}
\begin{center}
	\includegraphics[width=2\columnwidth]{figures/system.pdf}
\end{center}
\caption{An overview of the system and codebase. TODO (SAL): Add the actual system diagram image.}
\label{fig:system}
\end{figure*}

@@

Our framework includes a model class that can be trained on certain data with certain features enabled. The model class supports training a libSVM, libLinear, and CRF classifier that can be used for prediction in the future. One of the nice things, about the model class is that it can be serialized and reloaded dynamically. This is a really nice capability because it allows you to train a large number of models on various subsets of the dat and using various different features to see which perform the best.

@@

@@

@@

>>>>

\begin{figure*}
\begin{center}
	\includegraphics[width=2\columnwidth]{figures/system.pdf}
\end{center}
\caption{An overview of the system and codebase.}
\label{fig:system}
\end{figure*}

@@

Our framework includes a model class that can be trained on certain data with certain features enabled. The model class supports training a libSVM, libLinear, and CRF classifier that can be used for prediction in the future. One of the nice things, about the model class is that it can be serialized and reloaded dynamically. This is a really nice capability because it allows you to train a large number of models on various subsets of the data and using various different features to see which perform the best.

@@

We stopped using libSVMs.

@@

Found that libSVM was not worth while to use

@@

It goes without saying that having more data is always nice. This is particularly true in our case because we were training on a relatively small data set and testing on a much larger one. In fact, an interesting avenue for future work is to switch our training and testing data sets so we are training on relatively larger data set.
